Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2023-10-26 README.Rmd
update README to html
README with flextable

---
title: ""
output: github_document
editor_options: 
  markdown: 
    wrap: sentence
always_allow_html: true
---

@@

```{r}
proj_history <-
  gert::git_tag_list() |>
  dplyr::rename(
    milestone = name,
    milestone_hash = commit) |>
  mutate(
    commit_hash = (\(x) purrr::pmap_chr(list(milestone, ref, milestone_hash), .f = function(milestone, ref, milestone_hash) {
      gert::git_commit_info(milestone_hash)$id
    }))()
  ) |>
  left_join(
    gert::git_log() |>
      rename(commit_hash = commit)
  ) |>
  mutate(
    milestone_link = paste0(get_git_url(), '/releases/tag/', milestone),
    link = commit_hash,
    commit_link = paste0(get_git_url(), '/tree/', commit_hash)
  )

reactable::reactable(
  proj_history |> select(milestone, timestamp = time, author, message, link),
  columns = list(
    milestone = reactable::colDef(html = TRUE, cell = function(value, index) {
      sprintf("<a href='%s' target='_blank'>%s</a>", proj_history$milestone_link[index], value)
    }),
    link = reactable::colDef(html = TRUE, cell = function(value, index) {
      sprintf("<a href='%s' target=' _blank'>%s</a>", proj_history$commit_link[index], value)
    })
  )
)
```
### Contact

>>>>

---
title: "Working memory performance in adverse environments: Enhanced, impaired, or intact?"
output: 
  github_document:
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r}
proj_history <-
  gert::git_tag_list() |>
  dplyr::rename(
    milestone = name,
    milestone_hash = commit) |>
  mutate(
    commit_hash = (\(x) purrr::pmap_chr(list(milestone, ref, milestone_hash), .f = function(milestone, ref, milestone_hash) {
      gert::git_commit_info(milestone_hash)$id
    }))()
  ) |>
  left_join(
    gert::git_log() |>
      rename(commit_hash = commit)
  ) |>
  mutate(
    milestone_link = paste0(get_git_url(), '/releases/tag/', milestone),
    link = commit_hash,
    commit_link = paste0(get_git_url(), '/tree/', commit_hash)
  ) |> 
  separate(message, into = c("message", "code"), sep = "code") |> 
  mutate(
    code = str_replace_all(code, "\\|\\>", "\\|\\>\\\n"),
    message = str_remove(message, "\\\nobject_hash.*$")
  )

flextable::flextable(proj_history) |> 
  flextable::autofit() |> 
  flextable::compose(
    j = "milestone",
    value = flextable::as_paragraph(
      flextable::hyperlink_text(x = milestone, url = milestone_link)
    )
  ) |> 
  flextable::compose(
    j = "link",
    value = flextable::as_paragraph(
      flextable::hyperlink_text(x = "Click here", url = commit_link)
    )
  ) |> 
  flextable::delete_columns(c("ref", "milestone_hash", "commit_hash", "files", "merge", "milestone_link", "commit_link"))
```

### Contact
